Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-11-26 Latex_files/Thesis/chapters/chapter 4/main.tex
updates to chp 4 & 2

>>>>

\subsection{QPD for angular displacement detection}

The next logical step is to consider whether or not a QPD can at 
all be utilised for detection of rotational motion. This has been
shown for nano-particles that exhibit periodic rotational motion
using by considering the difference in diagonal quadrants. The 
benefit of detecting rotational motion is that one can begin to 
build a better understanding about how angular momentum is 
transferred to a dimer which could be extended to more complex
particles.

At just a cursory glance it would appear that there is a clear
relationship between the QPD signal and the orientation of the 
dimer. If we look at the QPD signal produced by a dimer is 
rotated
